---
output:
  html_document: default
  pdf_document: default
---
## Combining tables

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(ggrepel)
library(dslabs)
library(table1) # for table generation
library('yarrr') # for color palettes
library(mice) # for missing value
library(corrplot) # for correlation plot
library(splines2) # for spline(year)
```

The information we need for a given analysis may not be in just one table. Here we use a simple example to illustrate the general challenge of combining tables.

```{r, include=FALSE}
data1999 <- read_csv("1999_data.csv")
data2001 <- read_csv("2001_data.csv")
data2003 <- read_csv("2003_data.csv")
data2005 <- read_csv("2005_data.csv")
data2007 <- read_csv("2007_data.csv")
data2009 <- read_csv("2009_data.csv")
data2011 <- read_csv("2011_data.csv")
data2013 <- read_csv("2013_data.csv")
```

```{r, include=FALSE}
names(data1999)[1] <- 'year'
names(data2001)[1] <- 'year'
names(data2003)[1] <- 'year'
names(data2005)[1] <- 'year'
names(data2007)[1] <- 'year'
names(data2009)[1] <- 'year'
names(data2011)[1] <- 'year'
names(data2013)[1] <- 'year'
data1999$year <- rep(1999, dim(data1999)[1])
data2001$year <- rep(2001, dim(data2001)[1])
data2003$year <- rep(2003, dim(data2003)[1])
data2005$year <- rep(2005, dim(data2005)[1])
data2007$year <- rep(2007, dim(data2007)[1])
data2009$year <- rep(2009, dim(data2009)[1])
data2011$year <- rep(2011, dim(data2011)[1])
data2013$year <- rep(2013, dim(data2013)[1])
```

```{r, include=FALSE}
head(data1999)
head(data2001)
head(data2003)
head(data2005)
head(data2007)
head(data2009)
head(data2011)
head(data2013)
```

```{r,include=FALSE}
data1999 <- data1999 %>% mutate(race = as.character(race))
data2001 <- data2001 %>% mutate(race = as.character(race))
data2003 <- data2003 %>% mutate(race = as.character(race))
data2005 <- data2005 %>% mutate(race = as.character(race))
```

```{r, include=FALSE}
data_all <- dplyr::bind_rows(data2007,data1999,data2001,data2003,data2005,data2009,data2011,data2013)
data_all <- data_all[order(data_all$year),]
#write.csv(data_all, file="yrbs.csv",row.names = FALSE)
```

```{r}
data_all <- read_csv("yrbs.csv")

data_all$race3 <- data_all$race2
data_all$race3[data_all$hispanic == 1
               & is.na(data_all$race2)] <- 'Hispanic or Latino'
data_all$race3[data_all$hispanic == 1
               & data_all$race2=='Multiple'] <- "Multiple - Hispanic"
data_all$race3[data_all$hispanic == 2
               & data_all$race2=='Multiple'] <- "Multiple - Non-hispanic"
data_all$race3[data_all$race3=='Multiple'] <- NA

data_all$bmi3 <- data_all$BMI2
data_all$bmi3[data_all$BMI2 == 1] <- "Very underweight"
data_all$bmi3[data_all$BMI2 == 2] <- "Slightly underweight"
data_all$bmi3[data_all$BMI2 == 3] <- "About the right weight"
data_all$bmi3[data_all$BMI2 == 4] <- "Slightly overweight"
data_all$bmi3[data_all$BMI2 == 5] <- "Very overweight"

data_all$uwcbs <- data_all$UWCBs
data_all$uwcbs[data_all$UWCBs == 1] <- 'Yes'
data_all$uwcbs[data_all$UWCBs == 0] <- 'No'


data_all$`weight management2`[data_all$`weight management2` == "Not trying to do anything"] <- "0"

```

```{r}
table1::label(data_all$bmi3) <- "BMI - Weight Status"
table1::label(data_all$uwcbs) <- "Attempting UWCBs"

table1(~ bmi3 + uwcbs| factor(age2), data=data_all,
       caption = 'Table 1 Descriptive statistics of participant’s weight and UWCBs by age' )
```

```{r}
data_new <- data_all %>% filter(age2 > 13)
data_new$age3 <- factor(data_new$age2)
table1::label(data_new$sex2) <- "Sex"
table1::label(data_new$race3) <- "Race"
table1::label(data_new$age3) <- "Age (years)"
table1(~ sex2 + age3 + race3 + bmi3 + uwcbs | as.factor(year), data=data_new,
        caption = 'Table 2 Demographics of participants by year' )
```

## Results
#### Preliminary Statistics
PartI Prevalence of UWCBs from 1999-2013
```{r}
# Distribution of BMI
table(data_new$year)
table(data_new$year[data_new$uwcbs=="Yes"])

n_total = c(table(data_new$year)[[1]],
          table(data_new$year)[[2]],
          table(data_new$year)[[3]],
          table(data_new$year)[[4]],
          table(data_new$year)[[5]],
          table(data_new$year)[[6]],
          table(data_new$year)[[7]],
          table(data_new$year)[[8]])

n_uwcbs =c(table(data_new$year[data_new$uwcbs=="Yes"])[[1]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[2]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[3]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[4]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[5]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[6]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[7]],
          table(data_new$year[data_new$uwcbs=="Yes"])[[8]])

n_prevalence = n_uwcbs/n_total
mean(n_prevalence)
sd(n_prevalence)
years = c('1999','2001','2003','2005','2007','2009','2011','2013')
temp_dat <- data.frame(n_prevalence,years)
```

```{r}
#############Here comes to female
data_female <- data_all %>% filter(sex == 1)
table(data_female$year)
table(data_female$year[data_new$uwcbs=="Yes"])

female_total = c(table(data_female$year)[[1]],
          table(data_female$year)[[2]],
          table(data_female$year)[[3]],
          table(data_female$year)[[4]],
          table(data_female$year)[[5]],
          table(data_female$year)[[6]],
          table(data_female$year)[[7]],
          table(data_female$year)[[8]])

female_uwcbs =c(table(data_female$year[data_female$uwcbs=="Yes"])[[1]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[2]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[3]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[4]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[5]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[6]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[7]],
          table(data_female$year[data_female$uwcbs=="Yes"])[[8]])

female_prevalence = female_uwcbs/female_total
mean(female_prevalence)
sd(female_prevalence)
#############Here comes to male
data_male <- data_all %>% filter(sex == 2)
table(data_male$year)
table(data_male$year[data_new$uwcbs=="Yes"])

male_total = c(table(data_male$year)[[1]],
          table(data_male$year)[[2]],
          table(data_male$year)[[3]],
          table(data_male$year)[[4]],
          table(data_male$year)[[5]],
          table(data_male$year)[[6]],
          table(data_male$year)[[7]],
          table(data_male$year)[[8]])

male_uwcbs =c(table(data_male$year[data_male$uwcbs=="Yes"])[[1]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[2]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[3]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[4]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[5]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[6]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[7]],
          table(data_male$year[data_male$uwcbs=="Yes"])[[8]])

male_prevalence = male_uwcbs/male_total
mean(male_prevalence)
sd(male_prevalence)

temp_dat <- data.frame(n_prevalence,years,male_prevalence,female_prevalence)
```

```{r}
barplot(n_prevalence~years,data=temp_dat,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"
                #,piratepal("pony", trans =.4, length.out = 3)
                ),
     #col = piratepal("pony", trans =.4, length.out = 8),
     ylim = c(0.1,0.3),
     xpd=FALSE, width=0.9,
     border = "white",
     xlab = 'Year', ylab = 'Frequency',
     main='Prevalence of UWCBs')
lines(temp_dat$female_prevalence, col='hot pink', lwd=1.5)
lines(temp_dat$male_prevalence,type='l',col='blue', lwd=1.5)
legend('topright', lwd=1.5, col=c('hotpink','blue'),
       legend=c('Female','Male'), box.col='white')
```

Self-perceived weight bias
```{r, warning=FALSE}
table1(~ `self-perceived weight bias`|bmi3, data=data_new,
       caption = 'Table 4 Descriptive statistics of self-perceived weight bias by BMI' )
```

```{r, warning=FALSE}
table1(~ `self-perceived weight bias`|year*bmi3, data=data_new,
       caption = 'Table 4 Descriptive statistics of self-perceived weight bias by BMI stratified by years' )
```

```{r}
boxplot(data_new$`self-perceived weight bias` ~ 
          factor(data_new$BMI2,
                 labels = c("severe/moderate underweight", "mild underweight",
                            "normal range", "overweight", "obesity")),
        col=  piratepal("pony",trans =.4), na.rm = TRUE,
        xlab = "BMI Category", ylab = "Self-perceived Weight Bias",
        main = 'Figure 2-1: Self-perceived weight bias by BMI',
        cex.axis = 0.54)
legend('topright', c("severe/moderate underweight", "mild underweight",
               "normal range", "overweight", "obesity"),
       fill = piratepal("pony",trans =.4), cex=0.7)
```

Take a look at pirateplot
```{r}
pirateplot(formula = `self-perceived weight bias` ~ 
             factor(BMI2, labels = c("severe/moderate underweight", "mild underweight",
                                     "normal range", "overweight", "obesity")),
           data = data_new,
           pal=  piratepal("pony"), 
           xlab = "BMI Category", ylab = "Self-perceived Weight Bias",
           main = 'Figure 2-2: Self-perceived weight bias by BMI',
           cex.axis = 0.77, cex.names = 0.54,
           avg.line.lwd = 3,
           point.cex=0.5, point.lwd=0.5, point.o=0.5, point.col=gray(.1))
legend('topright', c("severe/moderate underweight", "mild underweight",
               "normal range", "overweight", "obesity"),
       fill = piratepal("pony",trans =.5), cex=0.7)
```

```{r}
data_bmi1 <- data_all %>% filter(BMI2 == 1)
data_bmi2 <- data_all %>% filter(BMI2 == 2)
data_bmi3 <- data_all %>% filter(BMI2 == 3)
data_bmi4 <- data_all %>% filter(BMI2 == 4)
data_bmi5 <- data_all %>% filter(BMI2 == 5)


mean(data_bmi1$`self-perceived weight bias`,na.rm=TRUE)
mean(data_bmi2$`self-perceived weight bias`,na.rm=TRUE)
mean(data_bmi3$`self-perceived weight bias`,na.rm=TRUE)
mean(data_bmi4$`self-perceived weight bias`,na.rm=TRUE)
mean(data_bmi5$`self-perceived weight bias`,na.rm=TRUE)
```

Preliminary Analysis - Missing values

```{r}
dim(data_new)
sum(is.na(data_new[c(2:4, 7:20, 23:25)]))
na_data <- md.pattern(data_new[c(2:4, 7:20, 23:25)], plot = FALSE, rotate.name = TRUE)

m_data <- na_data[order(na_data[,ncol(na_data)], decreasing = TRUE),]
colnames(m_data)[ncol(na_data)] <- "sum"
m_data[1,]
```

Table 6 Missing-data patterns

| Variable | # of Missing | Variable | # of Missing |
|-----|----|-----|----|
| Age | 0 | Sex | 208 |
| Grade | 251 | Suicide |832|
| weight management | 1632 | self-perceived weight| 1895 |
| vomit/laxative | 2176 | diet pills | 2351 |
| marijuana | 2694 | fast | 3133 |
| drive_drink | 3188 | smoke_level | 3481 |
| smoke | 5357 | PE | 7476 |
| smoke_quit | 7565 | height | 7769 |
| weight | 7769 | alcohol  | 8713 |
| sexual | 8979 | condom | 10369 |
| sum | 85838 | | |

```{r}
# Do correlation test to assess whether the missingness indicator m_uwcbs is associated with other covariates
cor.test(data_new$m_uwcbs, data_new$BMI2)
cor.test(data_new$m_uwcbs, data_new$`self-perceived weight`)
```

#### Inferential Statistics Analysis
```{r}
#############Here comes to different bmi1 groups
table(data_bmi1$year)
table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])

bmi1_total = c(table(data_bmi1$year)[[1]],
               table(data_bmi1$year)[[2]],
               table(data_bmi1$year)[[3]],
               table(data_bmi1$year)[[4]],
               table(data_bmi1$year)[[5]],
               table(data_bmi1$year)[[6]],
               table(data_bmi1$year)[[7]],
               table(data_bmi1$year)[[8]])

bmi1_uwcbs =c(table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[1]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[2]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[3]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[4]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[5]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[6]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[7]],
              table(data_bmi1$year[data_bmi1$uwcbs=="Yes"])[[8]])

bmi1_prevalence = bmi1_uwcbs/bmi1_total
mean(bmi1_prevalence)
sd(bmi1_prevalence)

#############Here comes to different bmi groups
table(data_bmi2$year)
table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])

bmi2_total = c(table(data_bmi2$year)[[1]],
               table(data_bmi2$year)[[2]],
               table(data_bmi2$year)[[3]],
               table(data_bmi2$year)[[4]],
               table(data_bmi2$year)[[5]],
               table(data_bmi2$year)[[6]],
               table(data_bmi2$year)[[7]],
               table(data_bmi2$year)[[8]])

bmi2_uwcbs =c(table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[1]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[2]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[3]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[4]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[5]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[6]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[7]],
              table(data_bmi2$year[data_bmi2$uwcbs=="Yes"])[[8]])

bmi2_prevalence = bmi2_uwcbs/bmi2_total
mean(bmi2_prevalence)
sd(bmi2_prevalence)

#############Here comes to different bmi groups
table(data_bmi3$year)
table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])

bmi3_total = c(table(data_bmi3$year)[[1]],
               table(data_bmi3$year)[[2]],
               table(data_bmi3$year)[[3]],
               table(data_bmi3$year)[[4]],
               table(data_bmi3$year)[[5]],
               table(data_bmi3$year)[[6]],
               table(data_bmi3$year)[[7]],
               table(data_bmi3$year)[[8]])

bmi3_uwcbs =c(table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[1]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[2]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[3]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[4]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[5]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[6]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[7]],
              table(data_bmi3$year[data_bmi3$uwcbs=="Yes"])[[8]])

bmi3_prevalence = bmi3_uwcbs/bmi3_total
mean(bmi3_prevalence)
sd(bmi3_prevalence)

#############Here comes to different bmi groups

table(data_bmi4$year)
table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])

bmi4_total = c(table(data_bmi4$year)[[1]],
               table(data_bmi4$year)[[2]],
               table(data_bmi4$year)[[3]],
               table(data_bmi4$year)[[4]],
               table(data_bmi4$year)[[5]],
               table(data_bmi4$year)[[6]],
               table(data_bmi4$year)[[7]],
               table(data_bmi4$year)[[8]])

bmi4_uwcbs =c(table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[1]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[2]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[3]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[4]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[5]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[6]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[7]],
              table(data_bmi4$year[data_bmi4$uwcbs=="Yes"])[[8]])

bmi4_prevalence = bmi4_uwcbs/bmi4_total
mean(bmi4_prevalence)
sd(bmi4_prevalence)

#############Here comes to different bmi groups

table(data_bmi5$year)
table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])

bmi5_total = c(table(data_bmi5$year)[[1]],
               table(data_bmi5$year)[[2]],
               table(data_bmi5$year)[[3]],
               table(data_bmi5$year)[[4]],
               table(data_bmi5$year)[[5]],
               table(data_bmi5$year)[[6]],
               table(data_bmi5$year)[[7]],
               table(data_bmi5$year)[[8]])

bmi5_uwcbs =c(table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[1]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[2]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[3]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[4]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[5]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[6]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[7]],
              table(data_bmi5$year[data_bmi5$uwcbs=="Yes"])[[8]])

bmi5_prevalence = bmi5_uwcbs/bmi5_total
mean(bmi5_prevalence)
sd(bmi5_prevalence)
```

```{r, warning=FALSE}
temp_dat <- data.frame(n_prevalence,years,male_prevalence,female_prevalence,
                       bmi1_prevalence,bmi2_prevalence,bmi3_prevalence,bmi4_prevalence,bmi5_prevalence)

plot( temp_dat$years,temp_dat$bmi1_prevalence, col=piratepal("pony", trans =.3)[1],
      lwd=2, type='line', ylim = c(0.05,0.4),
     xlab = 'Year', ylab = 'Frequency', main='Figure 3: Prevalence of UWCBs')
lines(temp_dat$years,temp_dat$bmi2_prevalence,
      col=piratepal("pony", trans =.3)[3], lwd=2)
lines(temp_dat$years,temp_dat$bmi3_prevalence,
      col=piratepal("pony", trans =.3)[2], lwd=2)
lines(temp_dat$years,temp_dat$bmi4_prevalence,
      col=piratepal("pony", trans =.3)[4], lwd=2)
lines(temp_dat$years,temp_dat$bmi5_prevalence,
      col=piratepal("pony", trans =.3)[5], lwd=2)
legend('topright', lwd=1.5, cex=0.8,
       col=piratepal("pony", trans =.3)[c(1,3,2,4,5)],
       legend=c('Very underweight', 'Slightly underweight', 'About the right weight',
                'Slightly overweight', 'Very overweight'))
```

```{r}
table1(~  uwcbs | bmi3*`weight management2`, data=data_new,
       caption = 'Table 2 Demographics of participants by year' )
```

```{r}
data_1999 <- data_all %>% filter(year == 1999)
data_2001 <- data_all %>% filter(year == 2001)
data_2003 <- data_all %>% filter(year == 2003)
data_2005 <- data_all %>% filter(year == 2005)
data_2007 <- data_all %>% filter(year == 2007)
data_2009 <- data_all %>% filter(year == 2009)
data_2011 <- data_all %>% filter(year == 2011)
data_2013 <- data_all %>% filter(year == 2013)
```


```{r, include=FALSE}
summary( glm(UWCBs ~ bmi3,
                 data = data_new, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_1999, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2001, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2003, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2005, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2007, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2009, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2011, family=binomial()))
summary( glm(UWCBs ~ bmi3,
                 data = data_2013, family=binomial()))
```

```{r}
OR_unadjusted = matrix(0,4,9)

OR_unadjusted[,1]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_1999, family=binomial())))[2:5]
OR_unadjusted[,2]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2001, family=binomial())))[2:5]
OR_unadjusted[,3]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2003, family=binomial())))[2:5]
OR_unadjusted[,4]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2005, family=binomial())))[2:5]
OR_unadjusted[,5]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2007, family=binomial())))[2:5]
OR_unadjusted[,6]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2009, family=binomial())))[2:5]
OR_unadjusted[,7]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2011, family=binomial())))[2:5]
OR_unadjusted[,8]=exp(coef(glm(UWCBs ~ bmi3,
                 data = data_2013, family=binomial())))[2:5]
OR_unadjusted[,9] = exp(coef(glm(UWCBs ~ bmi3,
                                 data = data_new, family=binomial())))[2:5]

rownames(OR_unadjusted) = c("BMI4:Slightly overweight",
                            "BMI2:Slightly Underweight",
                            "BMI5:Very overweight",
                            "BMI1:Very underweight")
colnames(OR_unadjusted) = c(years, "Overall")
```

```{r}
options(digits = 4)
OR_unadjusted
```

(12/27) overall unadjusted model with spline(year)
```{r}
uwcb.unadjusted.overall <- glm(UWCBs ~ bmi3,
                              data = data_new, family=binomial())
uwcb.unadjusted.bs <- glm(UWCBs ~ bmi3 + bSpline(year, df=5), data = data_new, family=binomial())
exp(coef(uwcb.unadjusted.bs))[2:5]
```

Inferential Analysis - other risk behaviors
```{r}
cor <- data_new %>%
  select(age, sex, drive_drink, suicide, smoke, alcohol2, marijuana2, sexual, condom2, PE, 
         BMI, `weight management`, UWCBs) %>%
   filter(!is.na(age)) %>%
  filter(!is.na(sex)) %>%
  filter(!is.na(drive_drink)) %>%
  filter(!is.na(suicide)) %>%
  filter(!is.na(smoke)) %>%
  filter(!is.na(alcohol2)) %>%
  filter(!is.na(marijuana2)) %>%
  filter(!is.na(sexual)) %>%
  filter(!is.na(condom2)) %>%
  filter(!is.na(PE)) %>%
  filter(!is.na(BMI)) %>%
  filter(!is.na(UWCBs))%>%
  filter(!is.na(`weight management`))

corr <- cor(cor, method = 'pearson')
col1=  colorRampPalette(c(piratepal("pony", length.out = 1), 'white', 'blue'))  
```


```{r}
corrplot(corr, method = 'color', tl.cex = 0.9, tl.col = 'black', col = col1(10)) 
corrplot(corr, method = 'number', number.cex = 0.7, tl.cex = 0.9, tl.col = 'black', col = col1(10))
```

```{r}
OR_adjusted = matrix(0,4,9)

OR_adjusted[,1]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                             data = data_1999,family=binomial())))[2:5]
OR_adjusted[,2]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2001, family=binomial())))[2:5]
OR_adjusted[,3]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2003, family=binomial())))[2:5]
OR_adjusted[,4]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2005, family=binomial())))[2:5]
OR_adjusted[,5]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2007, family=binomial())))[2:5]
OR_adjusted[,6]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2009, family=binomial())))[2:5]
OR_adjusted[,7]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2011, family=binomial())))[2:5]
OR_adjusted[,8]=exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                 data = data_2013, family=binomial())))[2:5]
OR_adjusted[,9] = exp(coef(glm(UWCBs ~ bmi3 + `weight management2`,
                                 data = data_new, family=binomial())))[2:5]

rownames(OR_adjusted) = c("BMI4:Slightly overweight",
                            "BMI2:Slightly Underweight",
                            "BMI5:Very overweight",
                            "BMI1:Very underweight")
colnames(OR_adjusted) = c(years, "Overall")
#View(as.data.frame(OR_adjusted))

OR_adjusted
```

(12/27) overall adjusted model with spline(year)
```{r}
uwcb.adj.overall <- glm(UWCBs ~ bmi3 + `weight management2`, data = data_new,
                    family=binomial())
uwcb.adj.bs <- glm(UWCBs ~ bmi3 + `weight management2` + bSpline(year, df=5),
                   data = data_new, family=binomial())
exp(coef(uwcb.adj.bs))[2:5]
```


```{r}
uwcb.adj.overall <- glm(UWCBs ~ bmi3 + `weight management2`, data = data_new,
                    family=binomial())
summary(glm(uwcb.adj.overall))

```


```{r}
OR_potential = matrix(0,4,9)

OR_potential[,1]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                             data = data_1999,family=binomial())))[2:5]
OR_potential[,2]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2001, family=binomial())))[2:5]
OR_potential[,3]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2003, family=binomial())))[2:5]
OR_potential[,4]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2005, family=binomial())))[2:5]
OR_potential[,5]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2007, family=binomial())))[2:5]
OR_potential[,6]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2009, family=binomial())))[2:5]
OR_potential[,7]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2011, family=binomial())))[2:5]
OR_potential[,8]=exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_2013, family=binomial())))[2:5]
OR_potential[,9] = exp(coef(glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                                 data = data_new, family=binomial())))[2:5]

rownames(OR_potential) = c("BMI4:Slightly overweight",
                            "BMI2:Slightly Underweight",
                            "BMI5:Very overweight",
                            "BMI1:Very underweight")
colnames(OR_potential) = c(years, "Overall")
#View(as.data.frame(OR_potential))

OR_potential
```


```{r}
coef( glm(UWCBs ~ sex2 + race3 + bmi3 + drive_drink2 + suicide2 +
                 smoke2 + alcohol2 + sexual2 + `weight management2`,
                 data = data_new, family=binomial()))

summary( glm(UWCBs ~ bmi3*`weight management2`, data = data_new, family=binomial()))
```

12/27/2021
Including 'year' effect in the model as a flexible form by using spline(year)
```{r}
uwcb.potential.overall <- glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                                smoke2 + alcohol2 + sexual2 + `weight management2`,
                              data = data_new, family=binomial())
#AIC = 63892
uwcb.potential.bs <- glm(UWCBs ~ bmi3 + sex2 + race3 + drive_drink2 + suicide2 +
                                smoke2 + alcohol2 + sexual2 + `weight management2`+
                           bSpline(year, df=5), data = data_new, family=binomial())
#AIC(df=3): 63832
#AIC(df=4): 63802
#AIC(df=5): 63799
#AIC(df=6): 63801

exp(coef(uwcb.potential.bs))[2:5]
```



